Simulation and visualization framework for decision making of climate mitigation \vspace{4pt} and adaptation strategies in new and existing urban development

### 2021-01-30 manuscript_wesbrook-bigmacc_BS2021.tex
Updates from Overleaf

\begin{figure}
    \centering
    \includegraphics{}
    \caption{A sample of how }
    \label{fig:sample_sequence}
\end{figure}

@@

\begin{table*}[h]
    \vspace{-5pt}   % Please use appropriate negative vspace to remove the space above/belovw the Table
    \caption{A two-column table.}
    \label{tab:model_table}
    \centering
    \begin{tabular}{| c | c | c | }
        \hline
        \bf{Heading 1} & \bf{Heading} 2 & \bf{Heading 3} \\
        \hline
        Entry 1 & Entry 2 & Entry 3 \\
        \hline
    \end{tabular}
    \vspace{-5pt}   % Please use appropriate negative vspace to remove the space above/belovw the Table
\end{table*}

@@

Two \textit{true} MACCs emerged in this study. The first represents a strategy-set that was chosen based on a high degree of adaptability present in, while also having a sizeable decrease in emissions. This was done under the worst-case climate scenario and the selected strategy-set (00011111) is highlighted in Figure \ref{fig:pareto_plot}. Figure \ref{fig:MACC_true_noDH_waterfall} describes how each strategy contributes to the overall decrease in emissions. The MACC is shown in Figure \ref{fig:MACC_true_noDH} where the first strategy, the installation of heat pumps to service space heating and cooling as well as domestic hot water, contributes to the bulk of the emissions reduction. This is due to the impact that moving away from the district heating system, which has the potential to use natural gas if heating and DHW load exceeds the district's heat pump capacity. The Figure has been altered in the vertical and horizontal access to then compare the scale of the remaining reduction measures, as only three measures actually contribute to emissions reductions. This point will be returned to more in the discussion, but raises that question about affordable marginal cost for significant abatement after fuel-switching has been achieved. This scenario only achieves 45\% emissions reduction over the baseline by 2080.

@@

A second \textit{true} MACC was generated under to abate as many emissions as possible under the assumption that the district heating system could not be abandoned and assuming the worst-case climate scenario. Figure \ref{fig:MACC_true_DH_waterfall} describes how each measure contributes to overall emissions reduction.

@@

\begin{figure}[hbpt]
    \centering
    \includegraphics[scale=1]{figures/true_macc_dh_waterfall.eps}
    \caption{Plotting marginal abatement cost and the adaptation metric to serve as a canvas for pathway planning.}
    \label{fig:MACC_true_DH_waterfall}
\end{figure}

%---------------------------------------------------------------------------------------
\section*{Discussion}

\subsection*{}

>>>>

\begin{figure}
    \centering
    \includegraphics{figures/sample_sequence.eps}
    \caption{Each scenario iterated through 256 combinations of strategy implementation.}
    \label{fig:sample_sequence}
\end{figure}

@@

@@

Two \textit{true} MACCs emerged in this study. The first represents a strategy-set that was chosen based on a high degree of adaptability present in, while also having a sizeable decrease in emissions. This was done under the worst-case climate scenario and the selected strategy-set (00011111) is highlighted in Figure \ref{fig:pareto_plot}. Figure \ref{fig:MACC_true_noDH_waterfall} describes how each strategy contributes to the overall decrease in emissions. The MACC is shown in Figure \ref{fig:MACC_true_noDH} where the first strategy, the installation of heat pumps to service space heating and cooling as well as domestic hot water, contributes to the bulk of the emissions reduction. This is due to the impact that moving away from the district heating system, which has the potential to use natural gas if heating and DHW load exceeds the district's heat pump capacity. The Figure has been altered in the vertical and horizontal access to then compare the scale of the remaining reduction measures, as only three measures actually contribute to emissions reductions. This point will be returned to more in the discussion, but raises that question about affordable marginal cost for significant abatement after fuel-switching has been achieved. This scenario only achieves 67\% emissions reduction over the baseline by 2080.

@@

A second \textit{true} MACC was generated under to abate as many emissions as possible under the assumption that the district heating system could not be abandoned and assuming the worst-case climate scenario. Figure \ref{fig:MACC_true_DH_waterfall} describes how each measure contributes to overall emissions reduction. The resulting MACC shows a more consistent scale of MAC and overall abatement between measures, but total abatement is only 8\% of the baseline's emissions.

@@

\begin{figure}[hbpt]
    \centering
    \includegraphics[scale=1]{figures/true_macc_DH_waterfall.eps}
    \caption{Plotting marginal abatement cost and the adaptation metric to serve as a canvas for pathway planning.}
    \label{fig:MACC_true_DH_waterfall}
\end{figure}

%---------------------------------------------------------------------------------------
\section*{Discussion}
The use of MACCs, \textit{true} and \textit{illustrative}, offers urban scale energy and development planning a way to compare different types of interventions for their merit as adaptation and mitigation interventions. This analysis is robust in that it simulates the technical and financial interaction of the proposed strategies under multiple climate change pathways and following different development trajectories. The first limitation lies in the not-so-explicit temporal interaction of the interventions. Each building was modeled as having its own unique construction and retrofit dates, which contribute to the emissions and total annualized cost profile for each run of the district energy model. While unique in their start and end date they are all set on a 30year time horizon for all elements replacement. While for some building technologies this may be a realistic time horizon for design-life, for many others it is not. Future efforts need to consider equipment and technology replacements more actively while also engaging the temporal simulation steps at more fine scales, possibly ten-years.

\subsection*{Strategy choice}
A major limitation is the framework underpinning this study is the finite space of strategy choice. We test eight strategies here that are applied generally across the district. Future efforts need to be more precise with strategy implementation based on building or site need.

\subsection*{Abatement after fuel-switching}
- possible solutions
- non economic frameworks

The context for this study sets up an interesting proposition within BC. The electrical grid is majority hydroelectric. Emissions within the building sector are therefore driven by natural gas use, either on site or within district systems. As the two \textit{true} MACC cases show that in order to reach large reductions over the baseline condition the use of natural gas must be eliminated.

This however raises the point of how abatement should continua once the significant reductions are made and systems are then relying on a near-carbon free grid. This study showed in testing rooftop photovoltaic that for this type of density, just rooftop panels are not going to generate significant amounts of energy or contribute to emissions reductions; in the worst-case climate scenario rooftop panels reduced emissions by 4.4\%.
